Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-08-20 paper.tex
references update, after the MLP has been included again
reviewing some text along the paper
including the recommend systems in the future works part (comment 3 by Rev.2): Closes #46

Overall, this study contributes to the literature by proposing the use
of different soft-computing standard techniques to solve a new
challenging problem. 
Moreover, proposed method, consisting in selecting features and
applying different models for different types of publishers could be
implemented, not only in the publishing  
industry, but also in other domains where the specificity of products
is similar such as novelty items or toys, and might be of interest to other academic researches and
industrial practitioners.  
% Antonio - I don't know if we should say this...

@@

As future work, it would be interesting to compare the obtained
forecasting results with those yielded by other soft-computing
methods, such as genetic programming or fuzzy logic. 
Moreover, even if the methods have been configured to obtain the best
forecasting results, it would be of interest carrying out some
automatic parameter-tuning procedure by means of optimisation
meta-algorithms \cite{huang2006ga,Mookiah2013_EA_Tuning,Shen2016_FFly_Tuning},  
% Antonio - changed to include KBS references
for instance.

@@

%********************************************************************************
\bibliographystyle{elsarticle-num}
\bibliography{refs}

>>>>

Overall, this study contributes to the literature by proposing the use
of different soft-computing standard techniques to solve a new
challenging problem. 
Moreover, proposed method, consisting in selecting features and
applying different models for different types of publishers could be
implemented, not only in the publishing  
industry, but also in other domains where the specificity of products
is similar such as novelty items or toys, and might be of interest to other 
academic researches and industrial practitioners.

@@

As future work, it would be interesting to compare the obtained
forecasting results with those yielded by other soft-computing
methods, such as genetic programming, recommend systems or fuzzy logic. 
Moreover, even if the methods have been configured to obtain the best
forecasting results, it would be of interest carrying out some
automatic parameter-tuning procedure by means of optimisation
meta-algorithms \cite{huang2006ga,Mookiah2013_EA_Tuning,Shen2016_FFly_Tuning},  
% Antonio - changed to include KBS references
for instance.

@@

%********************************************************************************
\bibliographystyle{elsarticle-num}
\bibliography{refs}
% TODO:
% the final list of references should be imported here from the .bbl file 
% obtained after compiling the main LaTeX file.
% And the previous line (\bibliography{refs}) has then to be commented.
